Concurrent Programming in Harmony

### 2021-12-30 book/paper.tex
Latest
Added nice picture for ABD

@@

\begin{figure}
\begin{code}
<{:input:../code/abdtest.hny}>
\end{code}
\caption{\harmonylink{code/abdtest.hny} Testing the code in \autoref{fig:abd}}
\label{fig:abdtest}
\end{figure}

@@

You will note that the second command prints a warning:
``\texttt{behavior warning: strict subset of specified behavior}.''
Thus, the set of behaviors that our algorithm generates is a subset
of the behavior that the specification allows.
\autoref{fig:boscodfa} shows the behavior, and indeed it is not the
same as the behavior of \autoref{fig:consensus}.
This is because in our algorithm the outcome is decided a priori if more than
twothirds of the processors have the same proposal, whereas in the
consensus specification the outcome is only decided a priori if the
processors are initially unanimous.

>>>>

\begin{figure}
\begin{code}
<{:input:../code/register.hny}>
\end{code}
\caption{\harmonylink{code/register.hny} An atomic read/write register}
\label{fig:register}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/abdtest.png}
\end{center}
\begin{code}
<{:input:../code/abdtest.hny}>
\end{code}
\caption{\harmonylink{code/abdtest.hny} Testing the code in \autoref{fig:abd}}
\label{fig:abdtest}
\end{figure}

@@

@@

Note that the second command prints a warning:
``\texttt{behavior warning: strict subset of specified behavior}.''
Thus, the set of behaviors that our algorithm generates is a subset
of the behavior that the specification allows.
\autoref{fig:boscodfa} shows the behavior, and indeed it is not the
same as the behavior of \autoref{fig:consensus}.
This is because in our algorithm the outcome is decided a priori if more than
twothirds of the processors have the same proposal, whereas in the
consensus specification the outcome is only decided a priori if the
processors are initially unanimous.  Another difference is that if the
outcome is decided a priori, all processors are guaranteed to decide.
